Improving Usability of Remote Access to Sensitive Data

### 2014-07-23 ccsw14/paper.tex
finished implementation section

\subsection{Security Goals and Threat Model}

@@

Suspendisse potenti. Donec ornare metus sem, vel semper arcu fermentum in. Nunc
vehicula eros turpis, ut rhoncus nunc sodales pulvinar. Duis sed est interdum,
semper mi a, cursus sapien. Nulla elementum congue purus, eu faucibus nibh
congue et. Ut diam metus, euismod ac quam in, gravida dictum turpis. Vivamus
hendrerit facilisis tempor. Curabitur hendrerit orci ac libero vestibulum, sit
amet dictum enim viverra. Nulla rutrum dolor ligula, nec rutrum massa suscipit
volutpat. Aliquam id mi at velit aliquet imperdiet at nec mi. Integer in massa
nec augue dapibus ullamcorper. Aliquam nec sollicitudin elit.

@@

>>>>

\subsection{Security Goals and Threat Model}
\label{sec:Threat Model}

@@

A prototype of the Data Capsules system has been developed using the KVM virtual
machine manager, which is built in to the Linux operating system, along with the
user-level counterpart application qemu to achieve virtualization.  A set of
Bash shell scripts were written to implement the basic operations for managing
Data Capsules VMs.  Although the current prototype does not fully support the
migration-based mode change described in this paper, migration-based switching
has been implemented and demonstrated, and the only remaining work is to fully
integrate it into the existing code.

End users may use either a convenient web interface, or call the scripts
directly in order to perform basic operations including creation and deletion of
VMs, running and stopping VMs, as well as switches between maintenance and
secure modes.

Although it could be argued that other, better choices for a virtual machine
manager exist on which to base such a demonstration system, it is the opinion of
the authors that no currently existing virtual machine manager is sufficiently
well written and designed so as to serve as an ideal choice, since there is no
x86-based hypervisor that is formally proven to be properly implemented and
secure.  The choice of KVM was for its ubiquity as part of the Linux operating
system along with ease of development.  However, as mentioned in Section
\ref{sec:Threat Model}, microkernels do exist which serve to demonstrate that
at least something close to such a robust, well-designed VMM could be made.

\subsection{Network Protections}

The Data Capsules prototype uses iptables rules to implement a simple set of
firewall rules for VMs.  All VMs on a machine reside on a bridged, private
network.  In secure mode, additional rules are imposed on the private IP address
of the VM, restricting all network access except that between the VM and the IP
address of the one or more servers containing the sensitive data, as written in
a simple configuration file.

Because limiting access to only a small set of servers eliminates access to
public DNS servers, for our prototype we configured the \texttt{/etc/hosts} file
on VM images to allow them to resolve the server domain names when in secure
mode.  More elegant solutions could be achieved by allowing access to a
custom purpose-built DNS server, or by using solutions like cloud-init, which is
available for Linux based virtual machines.

\subsection{Secure Storage Volume}

In order for a user's intermediate research to persist across sessions within
secure mode, a storage volume is attached upon entering secure mode.  This
volume is implemented as a disk image file, which is attached as an emulated USB
thumb drive.  From the user's perspective, this is a convenient access paradigm,
as one can imagine a virtual USB drive being ``plugged in" to the machine when
the user switches to secure mode, and then being removed when the user switches
back.

One currently unresolved issue with this approach, and any using a mounted disk
volume, is the issue of caching by the operating system of any changes to the
secure volume.  Since changes typically are not immediately written back to a
disk volume, this raises the possibility that a user could switch out of secure
mode before all data is written back, resulting in data loss.  Currently, we
warn users of the prototype before they switch out of secure mode that they must
detatch the secure volume or risk data loss.  In the future, we might include
software on preconfigured VMs that can help users know when it is safe to switch
out of secure mode.

\subsection{Releasing Research Results}

Since users ultimately require some method for releasing the results of their
research, qemu was configured to create a channel through the serial port on the
VM to a UNIX domain socket on the host machine.  A simple daemon was written
which runs on the secure machine to listen on this socket for any results to be
released.  It follows an extremely simple protocol that takes the file name,
file size, and file data and exports them to a database where they can then
undergo a review process.  We discuss potential approaches for automating this
review process for candidate release data in Section \ref{sec:Results Audit}

@@

%mode switch seamlessness (across machines)

%secure client access w/TPM
% -secure client
% -secure VNC connection

%managing migration speeds for performance & network

%automating part/all of result release audit
%\label{sec:Results Audit}

%evaluation plans and some preliminary results
